\chapter{Conclusion}
\label{chap:conclusion}

Today, more so than ever, having secure, usable ways of protecting our
data is of the utmost importance. Unfortunately, existing technologies
are failing us. Most data storage systems provide little security by
default. The technologies that do exist to secure data, like strong
cryptography, are challenging to use, especially in a manner that fits
our modern usage habits. Furthermore, we have been led to conflate
features with trust, or at least to forgo trust in favor of
features. How can we protect and control our data in a manner that is
easy to use, that is well suited to modern user cases, and that allows
us to control whom we chose to trust with our data while still
leveraging the rich set of features available on modern data-driven
services?  Custos aims to provide the basis of one possible answer to
these questions.

Custos's primary contributions include:

\begin{packed_desc}
\item[Trust-Separation Architecture:] For creating dedicated secret
  stores run by trusted providers
\item[``Secret Storage as a Service Platform'':] For providing a
  dedicated secret (i.e. encryption key) storage and access control
  service
\item[A generic, flexible access control scheme:] Including the use of
  access control chains for generalized access control specifications
  using a range of authentication primitives
\item[Custos protocol:] For standardizing the exchange of secrets and
  the authentication information required to access them
\item[Custos Server Design and Implementing:] Demonstrating the basics
  of Custos server design
\item[Several Proof-of-Concept Custos Applications:] Demonstrating the
  range of Custos use cases and the manner in which one might improve
  existing application through the use of Custos.
\end{packed_desc}

\section{Conclusions}

Custos provides a flexible, secure key:value storage
architecture. This architecture can be used to store secrets directly,
regulating access via flexible authentication primitives. It can also
be used as a component in a larger encryption-based data security
scheme, where Custos provides a logically centralized ``Key Storage as
a Service'' platform capable of making the associated encryption
systems more flexible, and thus more usable. The flexibility of the
Custos architecture allow it to solve a variety of modern security
problems, and forms the basis for a ``Trust as a Service'' security
model appropriate for a range of contemporary applications.

\subsection{Successes}

My experience with Custos thus far has underlined the flexibility of
the system. Custos's flexibility is primarily derived from two
attributes of the system: Custos's logically centralized nature, and
Custos's extensible authentication and access control scheme. The
centralization of Custos allows many services to rely on it as a
standardized security and access control system. The centralized
nature also supports multi-user, multi-device use cases that are not
possible in local, ad-hoc secret storage systems. The Custos access
control scheme, from the pluggable authentication modules supporting a
range of authentication parameters to the arbitrary access control
chains, allows for a wide range of access control intentions to be
expressed in a common, easy to use, language.

Custos's flexibility, in turn, enables usability improvements across a
range of application domains. Whether it's allowing for encryption
system that function across our myriad of modern devices and allow us
to securely share data with other users, or providing us with a
centralized personal data repository to which we can provide
controlled access for the web services of our choosing, Custos
encourages secure designs that also remain usable. While I have not
formally verified this usability, anecdotal experience using Custos to
protect my own data has shown it to enable usable, secure systems that
would not otherwise be achievable.

Finally, Custos provides a trust-separation architecture with a well
defined interface. This architecture could form the basis of
market-derived approach to security. Once we can separate trust from
unrelated functionality, it becomes far easier to select and reward
dedicated ``trust providers'' on the basis of their trustworthiness,
while still retaining the ability to select untrusted services on the
basis of the features they provide. If we truly wish to protect our
data, we must create an incentive-based system for providing
trustworthiness as a service to users, just as we currently have
systems that incentive providing features to users. Custos provides a
standardized, inter-provider-compatible architecture on which such an
ecosystem could be built.

\subsection{Challenges}

While Custos has its successes, it is certainly not without its
challenges. First and foremost, Custos does not eliminate the need for
trust, it simply isolates and it and makes it more flexibly
assignable. In order to gain many of the usability benefits of a
Custos-backed encryption system, you must still trust a third
party. While it is possible to operate your own Custos server, and
some may very well do that, doing so is not within realistic reach of
many end-users, and may very well negate many of the usability
benefits Custos provides. Trust is still necessary, Custos only helps
commoditize and regulate it.

Furthermore, Custos, like any new system, faces adoption
challenges. At this point in time, there are no mainstream systems
that utilize Custos. While I believe many systems could be refactored
to use Custos with minimal effort, the task of doing so, or convincing
others to do so, in still non-trivial. In order for Custos to succeed,
it must see at least moderately widespread standardization and
adoption. There must be readily available secure applications that
utilize Custos. Likewise, Custos providers must be easily available,
affordable, and numerous (in order to ensure some modicum of
trustworthiness through competition). Until Custos, or a similar
standardized secret storage system, becomes widely available, using
Custos in live production settings will remain challenging.

The performance overhead of using Custos is also not well
understood. For many end-user applications, raw performance is not the
primary concern, and there may exist a willingness to sacrifice some
performance in the name of increased security. That said, the overhead
of Custos across a range of applications has not been evaluated. Nor
have Custos performance bottlenecks and possible improvements been
identified. Such analysis will come with time and additional use of
Custos and Custos-backed applications.

Custos's authentication system, especially the access control chain
component, is highly flexible. But it remains to be seen whether or
not this flexibility will lead only to increased ease of use (a good
thing), or whether it risks giving the user too much freedom, making
it prone to misconfiguration and errors. Furthermore, the Custos
protocol is believed to be capable of supporting a wide range of
authentication primitives, but at this time, only a handful of
authentication primitives have actually been tested. Whether or not
the current format is capable of supporting more complex
authentication schemes, and how easily they might be implemented
within the Custos plugin framework, remains to be seen.

\section{Future Work}

The Custos work presented in this document represents the culmination
of the initial Custos design and implementation effort. It has
resulted in a usable secret storage service and the basis of a variety
of applications that leverage this service. That said, there is plenty
of work to be done to make Custos a fully production-ready and proven
system.

One of the key tenets of Custos design was usability, both the base
usability of Custos itself, and the increased usability of
applications leveraging Custos. I would like to conduct one or more
user studies evaluating the usability of Custos and Custos backed
applications. This might include measuring the success users have
building access control chains that meet their intentions (vs those
that subvert intentions through misconfiguration). It would also
likely include measuring the usability difference between a
traditional encryption system and a Custos-backed encryption
system. Backing up the Custos design principles with some solid
usability data, and adapting these principles where necessary to
increase usability, is a high priority for future Custos research.

I would also like to expand the reference Custos server
implementation, making it more robust, scalable, and widely
deployable. This will include switching to a high performance
key:value back-end, improving the Custos authentication plugin
interface, producing plugins for additional authentication primitives,
and improving the efficiency of the Custos access control chain
verification process. I would also like to explore availability and
redundancy features of the Custos server using various secret sharing
schemes.

I plan to build out several Custos-backed applications. This may
include either new native applications (like a Dropbox~\cite{dropbox}
encryption plugin) or the modification of existing applications (like
eCryptfs~\cite{eCryptfs}). These applications would allow further
testing of the Custos architecture and server in a production
environment, and might enable some of the use cases studies previously
mentioned.

Finally, Custos deserves a formal security audit to fully evaluate the
security of the server, client libraries, and communication
protocol. If Custos is to interact with secure systems, it must not
jeopardize the security of these systems. Fortunately the Custos code
base is still small enough that a manual audit is possible. Subjecting
Custos to automatic auditing tools or bounty-based exploit contests
might also yield interesting results with respect to the security of
the underlying systems. Issues and exploits discovered in such an
audit would be addresses in the design and implementation of future
Custos revisions.

\section{Discussion}

The cryptographer Bruce Schneier once wrote, ``It is insufficient to
protects ourselves with laws; we need to protect ourselves with
mathematics''~\cite{schneier1996applied}. He is, of course, referring
to strong cryptography as the great technological equalizer, allowing
anyone with access to a computer to achieve ``the same security as the
largest governments''~\cite{schneier2000secrets}. As it turns out,
this is not true\footnote{Schneier acknowledges the naivety of his
  original Utopian outlook on cryptography in his more recent
  works~\cite{schneier2000secrets}.}.

Not only has cryptography failed to enable the average person to
protect herself~\cite{green-challenge}, the belief that it can has led
to an increasing gap between the average user, who desires her data to
be protected, but who lacks the ability to protect it, and the elites
who are capable of protecting their own data while also preying on
those who can't. In his counter-culture manifesto, \textit{Computer
  Lib}, Ted Nelson states that, ``Guardianship of the computer can no
longer be left to the priesthood''~\cite{nelson1972computer}. It is
just as true today as it was when he wrote it. We can not afford to
forgo control of our data, leaving it to be picked over by the
``priesthood'' of crypto elite. We have already seen where that has
taken us in the revelations of Mr. Edward Snowden,
et. al.~\cite{GreenwaldPrism}: to a world where governments and
criminals (and governments turned criminals) will prey on the average
computer user who lacks the tools to adequately protect herself.

Furthermore, the rise of data-driven online serves has drastically
increased the exposure of our data to corporate interests. Users of
sites like Facebook or Twitter like to think they are the customers of
these services. They are not. They are the product. The customers are
the companies that buy user information or access to user eyeballs
from these services. This has created a colossal conflict of interest:
the companies we increasingly rely to store and safeguard our data
have a vested interest in profiting off of it. We must avoid this
conflict be creating a separate class of third parties, dedicated to
the protection of our data (likely in return for payment) to act as a
counter balance against the companies that desire to profit from our
data.

Custos is not about the mathematics. It is about making the
mathematics, and the resulting encryption techniques, available to
everyone. It is about increasing security through the commoditization
of trust, through an increase in usability, and through the
flexibility to support a diversity of end user intentions. We all want
to protect our data, and Custos aims to provide the basis for a set of
tools that will allow us to do that.

Security researchers can no longer afford to ignore the big
picture. Encryption alone is useless. Security requires a holistic
treatment. We must approach security from a technological, legal, and
anthropological standpoint. Only when we consider all of these factors
can we hope to make systems truly secure. Custos is one attempt to
accommodate a wider outlook in order to increase end user security. I
hope that other such project will follow and that Custos and related
efforts will succeed. We must reclaim security, reclaim encryption,
and reclaim control of our data. Our continued digital freedom, and by
proxy, our physical freedom, depend on doing just this.

%%  LocalWords:  Schneier Snowden et al Custos Custos's
