\documentclass[defaultstyle,11pt]{thesis}

\usepackage{array}
\usepackage{epsfig}
\usepackage{url}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{tabu}
\usepackage{tikz-qtree}
\usepackage{fancyvrb}

\usepackage{listings}
\lstset{
  language={},
  basicstyle=\footnotesize,
  numbers=left,
  numberstyle=\tiny,
  stepnumber=1,
  numbersep=5pt,
  showspaces=false,
  showstringspaces=false,
  showtabs=false,
  tabsize=4,
  captionpos=b,
  breaklines=true,
  breakatwhitespace=false,
  frame=single,
  frameround=tttt
}
\lstdefinelanguage{JavaScript}{
  keywords={break, case, catch, continue, debugger, default, delete,
    do, else, finally, for, function, if, in, instanceof, new, return,
    switch, this, throw, try, typeof, var, void, while, with, true,
    false, null},
  morecomment=[l]{//},
  morecomment=[s]{/*}{*/},
  morestring=[b]',
  morestring=[b]'',
  sensitive=true
}

\clubpenalty = 10000
\widowpenalty = 10000

%%%%%%%%%%%%   All the preamble material:   %%%%%%%%%%%%

\title{Custos: A Flexibly Secure Key-Value Storage Platform}

\author{Andy}{Sayler}

\otherdegrees{B.S.E.E., Tufts University, 2011}

\degree{Masters of Science in Computer Science}   %  #1 {long descr.}
       {M.S.C.S.}                                 %  #2 {short descr.}

\dept{Department of}        %  #1 {designation}
     {Computer Science}		%  #2 {name}

\advisor{Prof.}			%  #1 {title}
	{Dirk Grunwald}		%  #2 {name}

\reader{John Black}             %  2nd person to sign thesis
\readerThree{Eric Keller}       %  3rd person to sign thesis

\abstract{
  \OnePageChapter
  The magnitude of the digital data we create, store, and interact
  with on a daily basis is rapidly increasing. Simultaneously, we are
  demanding increasingly diverse use cases for our data: from syncing
  it across a variety of services and devices to sharing it with a
  number of organizations and friends. Securing our data and
  controlling who can access it is thus increasingly important, but
  also increasingly difficult. The existing tools we have for
  protecting our data, strong cryptography systems, are extremely
  inflexible. This inflexibility is due to cryptographic key storage
  being too tightly coupled with existing data encryption
  applications. This tight coupling makes these systems unusable for
  many of our desired use cases, leading to the underutilization of
  strong cryptography and the associated lack of protection and
  control of our data. I believe that this issue can be solved by
  providing a ``Key Storage as a Service'' system that separates
  secure key storage and access control from the underling encryption
  mechanisms. Toward this end, we present Custos: a flexible
  Cloud-based secret storage and access control service optimized for
  storing encryption keys and other secure secrets. Custos promotes
  the separation of functionally from trust, allowing us to rely on
  one service provider for their function while relying on another
  service provider for their trust. This separation opens up many
  doors related to the ways we create, store, and process digital
  data. In this work, I present the Custos design principles,
  architecture, and protocol specification. I also present several
  applications that leverage Custos to build more secure, flexible,
  and usable encryption and secret storage systems.}

\dedication[Dedication]{ To our forthcoming robot overlords. May they
  allow us humans to live out the last of our days in peace instead of
  immediately committing us to the robot-building work camps we most
  likely deserve.}

\acknowledgements{
  \OnePageChapter
  Thanks to Prof. Dirk Grunwald, Prof. Eric Keller, and Prof. John
  Black for their thoughts, help, and advisement completing this
  thesis. Thanks to Matthew Monaco for his comments and ideas related
  to this work. Thanks to Denali Hussin for her partnership and
  support throughout this work. Thanks to my colleagues, friends, and
  family for their continued input and support. Thanks to the good
  Mr. Edward Snowden and the fine spooks at the US National Security
  Agency (NSA) for making this work more relevant and widely
  applicable. }

%\ToCisShort	% use this only for 1-page Table of Contents

\LoFisShort	% use this only for 1-page Table of Figures
% \emptyLoF	% use this if there is no List of Figures

\LoTisShort	% use this only for 1-page Table of Tables
% \emptyLoT	% use this if there is no List of Tables

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%       BEGIN DOCUMENT...         %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\input macros.tex

\input chap_intro.tex
\input chap_uses.tex
\input chap_platform.tex
\input chap_clients.tex
\input chap_conclusion.tex

%%%%%%%%%   then the Bibliography, if any   %%%%%%%%%
\bibliographystyle{plain}	% or "siam", or "alpha", etc.
\nocite{*}		        % list all refs in database, cited or not
\bibliography{refs}		% Bib database in "refs.bib"

%%%%%%%%%   then the Appendices, if any   %%%%%%%%%
\appendix
\singlespacing
\input appx_messages.tex
\input appx_libcustos.tex

\end{document}

%%  LocalWords:  tex appx libcustos
