\chapter{Introduction}
\label{chap:intro}

Data is everywhere. Our devises produce it. Our web sites consume
it. Governments collect it and business request it. But in this ever
present whirlpool of data exchange, how can we stay in control of our
data? How can we ensure that those who we wish to can access it can
while preventing those who we do not from doing the same?

Fortunately, there are methods for securing our data: strong
cryptography systems like AES or RSA are perfectly capable of allowing
us to control exactly who can read our data. Unfortunately, these systems
are often difficult if not impossible for the average end user to
employ properly. Other times, they are simply treated like ``magic
fairy dust'' to be applied to various products in the name of
``just-add-crypto'' security with little heed paid to the security of
the implementation or components of the system.

How can we make encryption more usable? How can we make it more
accessible? And how can we accomplish both while maintain capability
with an array of modern use cases involving sharing, syncing, and
growing demand? Custos aims to provide an answer to these questions by
providing a secure key-value store that can be used to implement a
key-storage as a service platform.

\section{Overview}



\subsection{Separating Functionality from Trust}

Discuss separating what we use from who we trust. E.g. ``Using
facebook'' vs ``trusting Facebook''

\subsection{Key Storage as a Service}

Discuss separating key storage from encryption.

UUID : Data Encryption Key

\subsection{Flexibility and Usability}

Discuss need for variable levels of trust and flexible methods of
authentication. Discuss fitting security to desired uses. Avoiding
``one size fits all'' mentality.

\section{Background}

\subsection{Encryption}

Discuss symmetric and asymmetric encryption, uses, strengths,
weaknesses, etc.

Encryption = solved problem

Key Storage = The real challenge

\subsection{Secure Storage}

Discuss existing approaches (full stack systems, layered systems),
strengths, weaknesses, etc

\subsection{Human Factors}

Disuses existing usability challenges

\section{Related Work}

\subsection{Authentication Systems}

PAM, Shibboleth, OAuth, OpenID, SAML, Etc

\subsection{File Systems}

eCryptFS, LUKS, Oceanstore, Tahoe, AFS, Etc

\subsection{Other Systems}

Anything else?
