\documentclass[defaultstyle,11pt]{thesis}

\usepackage{array}
\usepackage{epsfig}
\usepackage{url}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{tabu}
\usepackage{tikz-qtree}
\usepackage{fancyvrb}

\usepackage{listings}
\lstset{
  language={},
  basicstyle=\footnotesize,
  numbers=left,
  numberstyle=\tiny,
  stepnumber=1,
  numbersep=5pt,
  showspaces=false,
  showstringspaces=false,
  showtabs=false,
  tabsize=4,
  captionpos=b,
  breaklines=true,
  breakatwhitespace=false,
  frame=single,
  frameround=tttt
}

%%%%%%%%%%%%   All the preamble material:   %%%%%%%%%%%%

\title{Custos: A Flexibly Secure Key-Value Storage Platform}

\author{A.}{Sayler}

\otherdegrees{B.S., Tufts University, 2011}

\degree{Masters of Science}     %  #1 {long descr.}
       {M.S., Computer Science} %  #2 {short descr.}

\dept{Department of}            %  #1 {designation}
     {Computer Science}		%  #2 {name}

\advisor{Prof.}			%  #1 {title}
	{Dirk Grunwald}		%  #2 {name}

\reader{John Black}             %  2nd person to sign thesis
\readerThree{Eric Keller}       %  3rd person to sign thesis

\abstract{
  \OnePageChapter
  The magnitude of the digital data we create, store, and interact
  with on a daily basis is rapidly increasing. Simultaneously, we are
  demanding increasingly diverse use cases for our data: from
  spreading it across a variety of services and devices to sharing it
  with a number of organizations and friends. Securing our data and
  controlling who can access it is thus increasingly important, but
  also increasingly difficult. The existing tools we have for
  protecting our data, strong encryption systems, are extremely
  inflexible. This inflexibility is due to encryption key storage
  being too tightly coupled with existing data encryption
  solutions. This tight coupling makes these systems unusable for many
  of our desired use cases, leading to the underutilization of strong
  encryption and the associated lack of protection and control of our
  data. We believe that this issue can be solved by providing a ``Key
  Storage as a Service'' system that separates secure key storage and
  access control from the underling encryption mechanisms. Toward this
  end, we present Custos: a flexible Cloud-based key-val storage and
  access control service optimized for storing encryption keys. Custos
  allows us to separate functionally from trust, allowing us to rely
  on one service provider for their function while relying on another
  service provider for their trust. This separation opens up many
  doors related to the ways we create, store, and process digital
  data.

}

\dedication[Dedication]{ To our forthcoming robot overlords. May they
  find it right and proper to allow us humans to live out the last of
  our days in peace instead of immediately committing us all to the
  work camps we as a species most likely deserve.}

\acknowledgements{
  \OnePageChapter
  Thanks to Prof. Dirk Gruwald and Prof. Eric Keller for their
  thoughts, help, and advisement completing this thesis. Thanks to
  Matthew Monaco for his comments and ideas related to this
  work. Thanks to Denali Hussin for her partnership and support
  throughout this work. Thanks to my friends and family for their
  continued input and support.
}

% \IRBprotocol{E927F29.001X}	% optional!

\ToCisShort	% use this only for 1-page Table of Contents

\LoFisShort	% use this only for 1-page Table of Figures
% \emptyLoF	% use this if there is no List of Figures

\LoTisShort	% use this only for 1-page Table of Tables
% \emptyLoT	% use this if there is no List of Tables

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%       BEGIN DOCUMENT...         %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\input macros.tex

\input chap_intro.tex
\input chap_uses.tex
\input chap_platform.tex
\input chap_clients.tex
\input chap_conclusion.tex

%%%%%%%%%   then the Bibliography, if any   %%%%%%%%%
\bibliographystyle{plain}	% or "siam", or "alpha", etc.
\nocite{*}		        % list all refs in database, cited or not
\bibliography{refs}		% Bib database in "refs.bib"

%%%%%%%%%   then the Appendices, if any   %%%%%%%%%
\appendix
\input appx_messages.tex
\input appx_libcustos.tex

\end{document}
