\section{Conclusions and Future Work}
\label{sec:conclusion}

Encryption key storage is too tightly coupled with existing encrypted
file system solutions. This tight coupling makes these systems
inflexible and thus unsuitable for many of our required use cases.
Such inflexibility leads to the underutilization of data encryption by
vast portions of the user base at a time when encryption is becoming a
more and more important tool for retaining control of our data. We
believe that this issue can be solved by providing a ``Key Storage as
a Service'' system that separates encryption key storage and access
control from the underlying encryption mechanisms that use these
keys. Custos provides this flexible Cloud-based key storage service.

We are currently working on building a full Custos prototype that
integrates with a basic encrypted file system~\cite{sayler-os-encfs}
built atop the Linux FUSE API. We hope to use this prototype to refine
the structure of both the management and key access APIs and to prove
out our modular authentication and requirements framework. Going
forward, we hope to provide example Custos integrations with a variety
of existing secure file systems, from systems like eCryptfs to systems
like OceanStore. We plan to use these implementations to demonstrate
how Custos can extend the flexibility and usability of a variety of
encryption solutions across a variety of use cases. We also plan to
further analyze the threat vectors inherent to a ``Key Storage as a
Service'' system and provide suggestions for practically mitigating
these threats in Custos deployments. We have plans to explore a
multi-provider Custos system that reduces the trust required for each
Custos server in favor of distributing portions of each key across
multiple servers. We hope to investigate the usability of Custos in a
variety of real-world use cases.
